\chapter{Requirements}\label{requirements}

The existing solutions have provided a basis for identifying the
potential problems the system must overcome. Along with other sources
and other base requirements a set of more formal requirements are listed
below.
\section{TO BE WRITTEN}

  stuff to go here

\subsection{Requirement 1}\label{requirement-1}

The application must store notes about the application in various
separate ``files'' within the system

brief reason for why this is a requirement

\subsection{Requirement 2}\label{requirement-2}
The ``files'' stored within the system must be able to store code and also
notes in a format more easily read by humans.

\subsection{Requirement 3}\label{requirement-3}
The application should be easily accessible from multiple operating systems
not necessarily Microsoft Windows.

\subsection{Requirement 4}\label{requirement-4}
The application should have the ability to view the results of queries executed on the
system in table form.

(Optional) The ability to detect the type of result and view it in a
more suitable form. The more suitable form could be anything from a
graph to folder structure to a specific viewer for xml documents.

\subsection{Requirement 5}\label{requirement-5}

The application should have a mechanism for organizing related files in
a hierarchy. Files that are about a part of the system should be stored
in the same place in the system.

\subsection{Requirement 6}\label{requirement-6}
The application should save the previous versions of the files stored within. These
versions should allow editing and saving over newer versions if needed.

\subsection{Requirement 7}\label{requirement-7}
The application should allow for multiple files to
be open at once and viewed at the same time. This can be done in a free
sized window mode or windows listed vertically or horizontally.

\subsection{Requirement 8}\label{requirement-8}
The application should allow for searching for strings in
files.

(Optional) The ability to view in each of the search results, where the
matched text is. And the ability to open the file from the search
results.

\subsection{Requirement 9}\label{requirement-9}
The application should allow for the easy
comparison of the results of the queries. Historic results of the
queries should be shown as a diff or side by side with newly executed

\section{Use cases of the system}\label{use-cases-of-the-system}

The use cases of the system will detail how the system is to be used by
its users. The primary users of the system as discussed is the
developers of the projects themselves. This restriction of the users of
the system and their interaction with it makes the system more simple to
design as there are less interaction to model in the system.

\subsection{Use case 1}\label{use-case-1}

Developer wants to document information about a development.

\subsection{Use case 2}\label{use-case-2}

Developer needs to view all documents regarding a project stored in the
system.

\subsection{Use case 3}\label{use-case-3}

Developer needs to find reference to a particular item within the system
but is unfamiliar with the specific location or other detail

\subsection{Use case 4}\label{use-case-4}

Developer has to find specific details of a system previously worked on
in order to maintain it.

\subsection{Use case 5}\label{use-case-5}

Developer wants to view and compare previous versions of some code
within the database

\subsection{Use case 6}\label{use-case-6}

Developer want to view the history of the notebook. There is a
particular entity of the system e.g.~table that they want to view the
history. i.e.~how the entity has evolved in the past.

\subsection{Use case 7}\label{use-case-7}

The developer wants to find the places a particular entity is used
within the system to better understand how the changes planned could
effect the system as a whole. AKA (impact
analysis){[}https://en.wikipedia.org/wiki/Change\_impact\_analysis{]}. *
cite impact analysis* \#\# Development priority of requirements
Discussion of importance of requirements identified above, put into
order and possibly identify partial fulfillment ideas
